Simulation study in rectangular domain

### 2024-04-16 R/simulation_study/simulation_study_rect.Rmd
changes in simulation_study_rect

```{r global variables}
#number of batch
N_BATCH=10

@@

#duration of each track in hour
TMAX=1*24

@@

```{r high error samples, cache=TRUE,results='hide'}
#setup parallel backend to use many processors
cores=detectCores()
cl <- makeCluster(cores[1]-1) #not to overload your computer
registerDoParallel(cl)

@@

```{r estimate te DistanceShore for low error samples,cache=TRUE}
#estimation with tensor splines
formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,DistanceShore,k=SP_DF,bs="cs"))

crcvm_rect_hf_ne2=list()
for (k in 1:N_BATCH) {
  m <- SDE$new(formulas = formulas,data = data_rect_hf_ne[[paste("BATCH"),k,sep=""]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H0_hf))
  m$fit(method="BFGS")
  crcvm_rect_hf_ne2[[paste("BATCH",k,sep="")]]<-m
}
```

@@

```{r estimate te ExpShore for high error samples, cache=TRUE}
#estimation with tensor splines
formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,ExpShore,k=SP_DF,bs="cs"))

crcvm_rect_hf_e1=list()
for (k in 1:N_BATCH) {
  m <- SDE$new(formulas = formulas,data = data_rect_hf_e[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H0_hf))
  m$fit(method="BFGS")
  crcvm_rect_hf_e1[[paste("BATCH",k,sep="")]]<-m
}
```

@@

```{r estimate te DistanceShore for high error samples,cache=TRUE}
#estimation with tensor splines
formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,DistanceShore,k=SP_DF,bs="cs"))

crcvm_rect_hf_e2=list()

for (k in 1:N_BATCH) {
  m <- SDE$new(formulas = formulas,data = data_rect_hf_e[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H0_hf))
  m$fit(method="BFGS")
  crcvm_rect_hf_e2[[paste("BATCH",k,sep="")]]<-m
}
```

>>>>

```{r global variables}
#number of batch
N_BATCH=2

@@

#duration of each track in hour
TMAX=0.5*24

@@

```{r parallel generate hf high error samples, cache=TRUE,results='hide'}
#setup parallel backend to use many processors
cores=detectCores()
cl <- makeCluster(cores[1]-1) #not to overload your computer
registerDoParallel(cl)

@@

```{r estimate te DistanceShore for low error samples,cache=TRUE}

crcvm_rect_hf_ne2<- foreach(i=1:N_BATCH,.packages=c("smoothSDE")) %dopar% {
  #estimation with tensor splines
  formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,DistanceShore,k=SP_DF,bs="cs"))
  par0 <- c(0,0,1,1,0)
  m <- SDE$new(formulas = formulas,data = data_rect_hf_ne[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H0_hf))
  m$fit(method="BFGS")
  m 
}

names(crcvm_rect_hf_ne2)=paste("BATCH",1:N_BATCH,sep="")
```

@@

```{r estimate te ExpShore for high error samples, cache=TRUE}

crcvm_rect_hf_e1<- foreach(i=1:N_BATCH,.packages=c("smoothSDE")) %dopar% {
  #estimation with tensor splines
  formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,ExpShore,k=SP_DF,bs="cs"))
  par0 <- c(0,0,1,1,0)
  m <- SDE$new(formulas = formulas,data = data_rect_hf_e[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H0_hf))
  m$fit(method="BFGS")
  m 
}

names(crcvm_rect_hf_e1)=paste("BATCH",1:N_BATCH,sep="")
```

@@

```{r estimate te DistanceShore for high error samples,cache=TRUE}

crcvm_rect_hf_e2<- foreach(i=1:N_BATCH,.packages=c("smoothSDE")) %dopar% {
  #estimation with tensor splines
  formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,DistanceShore,k=SP_DF,bs="cs"))
  par0 <- c(0,0,1,1,0)
  m <- SDE$new(formulas = formulas,data = data_rect_hf_e[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H0_hf))
  m$fit(method="BFGS")
  m 
}

names(crcvm_rect_hf_e2)=paste("BATCH",1:N_BATCH,sep="")
```
